\newpage

\setcounter{secnumdepth}{0}
\section{Список использованных источников}
\begingroup
\renewcommand{\section}[2]{}
\begin{thebibliography}{99}

\bibitem{frank1956algorithm}
Frank M., Wolfe P. An algorithm for quadratic programming // Naval Research Logistics Quarterly. 1956. Vol. 3. No. 1--2. P. 95--110.

\bibitem{jaggi2013revisiting}
Jaggi M. Revisiting Frank--Wolfe: Projection-Free Sparse Convex Optimization // Proceedings of the 30th International Conference on Machine Learning. 2013. Vol. 28. P. 427--435.

\bibitem{braun2022conditional}
Braun G., Pokutta S., Tu S., Wright S. Blended conditional gradients: the unconditioning of conditional gradients // SIAM Journal on Optimization. 2022.

\bibitem{patriksson2015traffic}
Patriksson M. The Traffic Assignment Problem: Models and Methods. Dover Publications, 2015.

\bibitem{mitradjieva2013stiff}
Mitradjieva M., Lindberg P. O. The Stiff Is Moving: Conjugate Direction Frank--Wolfe Methods with Applications to Traffic Assignment // Transportation Science. 2013. Vol. 47. No. 2. P. 280--293.

\bibitem{fukushima1984modified}
Fukushima M. A modified Frank--Wolfe algorithm for solving the traffic assignment problem // Transportation Research Part B: Methodological. 1984. Vol. 18. No. 2. P. 169--177.

\bibitem{arrache2008accelerating}
Arrache S., Ouafi R. Accelerating Convergence of the Frank--Wolfe Algorithm for Solving the Traffic Assignment Problem // International Journal of Computer Science and Network Security. 2008. Vol. 8. No. 5. P. 181--186.

\bibitem{ignashin2024modifications}
Игнашин И. Н., Ярмошик Д. В. Модификации алгоритма Frank--Wolfe в задаче поиска равновесного распределения транспортных потоков // Компьютерные исследования и моделирование. 2024. Т. 16. No. 1. С. 53--68. DOI: \url{https://doi.org/10.20537/2076-7633-2024-16-1-53-68}.

\bibitem{bstabler}
Stabler B. Transportation Networks for Research Core Team. TransportationNetworks repository. URL: \url{https://github.com/bstabler/TransportationNetworks}.

\bibitem{jaggi2012blockcoordfw}
Jaggi M., Lacoste-Julien S., Schmidt M. Block-Coordinate Frank--Wolfe Optimization for Structural SVMs // Proceedings of the 30th International Conference on Machine Learning. 2013.

\bibitem{lacoste2013block}
Lacoste-Julien S., Jaggi M., Schmidt M., Pletscher P. Block-Coordinate Frank--Wolfe Optimization for Structural SVMs // Proceedings of the 30th International Conference on Machine Learning. 2013. P. 53--61.

\bibitem{ignashin2026stochastic}
Ignashin I., Yarmoshik D., Raigorodskii A. Stochastic Origin Frank--Wolfe Method for Traffic Assignment // Journal of Mathematical Sciences. 2025. Vol. 295. No. 2. P. 170--184. DOI: \url{https://doi.org/10.1007/s10958-025-08157-6}.

\bibitem{wai2017decentralized}
Wai H.-T., Lafond J., Scaglione A., Moulines E. Decentralized Frank--Wolfe Algorithm for Convex and Nonconvex Problems // IEEE Transactions on Automatic Control. 2017. Vol. 62. No. 11. P. 5522--5537.

\bibitem{vedernikov2023decentralized}
Vedernikov R., Rogozin A., Gasnikov A. Decentralized Conditional Gradient Method over Time-Varying Graphs // arXiv preprint arXiv:2307.10978. 2023.

\bibitem{beckmann1956studies}
Beckmann M., McGuire C. B., Winsten C. B. Studies in the Economics of Transportation. Yale University Press, 1956.

\bibitem{wardrop1952road}
Wardrop J. G. Some theoretical aspects of road traffic research // Proceedings of the Institution of Civil Engineers. 1952. Vol. 1. No. 3. P. 325--362.

\bibitem{bpr1964traffic}
Bureau of Public Roads. Traffic Assignment Manual. U.S. Department of Commerce, Urban Planning Division, 1964.

\bibitem{sheffi1985urban}
Sheffi Y. Urban Transportation Networks: Equilibrium Analysis with Mathematical Programming Methods. Prentice-Hall, 1985.

\bibitem{leblanc1985improved}
LeBlanc L. J., Morlok E. K., Pierskalla W. P. An improved method for the solution of the transportation network equilibrium problem // Transportation Science. 1975. Vol. 9. No. 4. P. 309--318.

\bibitem{luenberger1984linear}
Luenberger D. G. Linear and Nonlinear Programming. Addison-Wesley, 1984.

\bibitem{bertsekas1999nonlinear}
Bertsekas D. P. Nonlinear Programming. Athena Scientific, 1999.

\bibitem{nesterov1983method}
Nesterov Y. A method for solving the convex programming problem with convergence rate $O(1/k^2)$ // Soviet Mathematics Doklady. 1983. Vol. 27. No. 2. P. 372--376.

\bibitem{nesterov2018lectures}
Nesterov Y. Lectures on Convex Optimization. Springer, 2018.

\bibitem{pedregosa2020linearly}
Pedregosa F., Negiar G., Askari A., Jaggi M. Linearly convergent Frank--Wolfe with backtracking line-search // Proceedings of the 23rd International Conference on Artificial Intelligence and Statistics. 2020. P. 1--10.

\bibitem{pearlmutter1994fast}
Pearlmutter B. A. Fast exact multiplication by the Hessian // Neural Computation. 1994. Vol. 6. No. 1. P. 147--160.

\bibitem{jax2018github}
Bradbury J., Frostig R., Hawkins P., Johnson M. J., Leary C., Maclaurin D., Wanderman-Milne S. JAX: composable transformations of Python+NumPy programs. 2018. URL: \url{https://github.com/google/jax}.

\bibitem{lecun1998mnist}
LeCun Y., Cortes C., Burges C. The MNIST database of handwritten digits. 1998. URL: \url{http://yann.lecun.com/exdb/mnist/}.

\bibitem{dua2019uci}
Dua D., Graff C. UCI Machine Learning Repository. University of California, Irvine, School of Information and Computer Sciences, 2019.

\bibitem{tibshirani1996regression}
Tibshirani R. Regression shrinkage and selection via the lasso // Journal of the Royal Statistical Society: Series B. 1996. Vol. 58. No. 1. P. 267--288.

\end{thebibliography}
\endgroup
\setcounter{secnumdepth}{3}
